Untitled

### 2014-10-18 EducProposal.Rmd
Tried making a table for the proposal document

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
date: "October 17, 2014"
author: "Sam Dundon and Thierry Racaud"
output: html_document
bibliography:
  - Main.bib
---
* * * 
```{r echo=FALSE,cache=TRUE,include=FALSE}
# Set working directory
setwd('~/DataAnalysis/')

>>>>

---
title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
date: "October 17, 2014"
author: "Sam Dundon and Thierry Racaud"
output: html_document
bibliography:
  - Main.bib
---
* * * 
```{r echo=FALSE, cache=TRUE, include=FALSE}
# Set working directory
setwd('~/DataAnalysis/')

### 2014-10-18 TrialFile.Rmd
Tried making a table for the proposal document

>>>>

<table>
<tr class="header">
<th align="left"> </th>
<th align="left"> </th>
</tr>
<tr class="odd">
<td align="left">Finance</td>
<td align="left">Government Policy</td>
<td align="left">Entrepreneurial Education and Training</td>
<td align="left">Research and Development Transfer (R & D)</td>

</tr>
<tr class="even">
<td align="left">Commercial and professional infrastructure</td>
<td align="left">Internal Market openness</td>
<td align="left">Physical infrastructure and services</td>
<td align="left">Cultural and social norms </td>
</tr>
</table>
